\documentclass{doc}

\setname{Patrick Hanford}{}
\setmobile{}
\setmail{patrick@phanford.dev}
\setlinkedinaccount{https://linkedin.com/in/phanford}
\setgithubaccount{https://github.com/codespent}
\setwebsite{https://phanford.dev}
\setthemecolor{MidnightBlue}


\begin{document}

%Create header
    \headerview
    \vspace{1ex} % white space
%
    \section{Skills}
    \newcommand{\skillone}{\createskill{Languages}{Python \cpshalf JavaScript \cpshalf TypeScript \cpshalf C\# \cpshalf Go \cpshalf Elixir \cpshalf Kotlin}}
    %
    \newcommand{\skilltwo}{\createskill{Frontend}{React \cpshalf Vue \cpshalf NextJS \cpshalf React Native \cpshalf TailwindCSS}}
    %
    \newcommand{\skillthree}{\createskill{Backend}{Django \cpshalf Flask \cpshalf FastAPI \cpshalf DotNet \cpshalf Entity Framework \cpshalf Phoenix \cpshalf GraphQL}}
    %
    \newcommand{\skillfour}{\createskill{Cloud/DevOps}{AWS \cpshalf GCP \cpshalf Azure \cpshalf Docker \cpshalf GitHub Actions}}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour}
    \vspace{-3mm} % reduces whitespace!
    %
%
    \section{Experience}
    %
    \datedexperience{Ford Motors International}{Sep 2024 - Dec 2025}
    \explanation{Fullstack Software Engineer}{}
    \vspace{3mm}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Worked in the Quality Assurance sector building internal tools that enable Ford's Quality teams representing ~12k users.

        \smallskip
        \coloredbullet\ %
        Built Text2SQL service from scratch, enabling natural language database queries and opening a new enterprise customer segment for the generative AI platform.

        \smallskip
        \coloredbullet\ %
        Optimized RAG pipeline APIs (Flask/FastAPI), reducing response latency by 90\% (1m14s to 7.2s) while scaling to handle 3x payload volume.

        \smallskip
        \coloredbullet\ %
        Built and integrated various Grafana dashboards for identifying performance optimizations within the entirety of our generative AI platform.

        \smallskip
        \coloredbullet\ %
        Built APIs that adhered to craftmanship standards from vendors such as 42Crunch, Snyk, SonarQube, and more.

        \smallskip
        \coloredbullet\ %
        Built dynamic data visualization layer using Chart.js, transforming static table outputs into interactive charts from LLM responses.

        \smallskip
        \coloredbullet\ %
        Designed async form component library with virtual scroll and incremental loading, adopted as standard across 12+ micro-frontend applications.

        \smallskip
        \coloredbullet\ %
        Rebuilt legacy data aggregation platform that enabled more comprehensive results with 43\% fewer queries and 85\% fewer user actions; increasing individual analyst productivity by up to 38\%.

        \smallskip
        \coloredbullet\ %
        Established code review standards and CI/CD guardrails, decreasing production incidents by 40\% over 6 months.

        \bigskip
    }
    %
    \datedexperience{Robert Half International}{Feb 2020 - Mar 2024}
    \explanation{Fullstack Software Engineer}{}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Migrated Angular Cordova mobile app to React Native, reducing build times by 70\% and achieving 99.5\% crash-free sessions across iOS and Android.

        \smallskip
        \coloredbullet \ %
        Took ownership of a multi-purpose DotNet API and integrated new endpoints to spec provided from various teams interface with this API.

        \smallskip
        \coloredbullet\ %
        Architected multi-database sync system (SQL Server, Postgres, MySQL) using Serenity framework, consolidating data from 8 legacy sources into unified reporting.

        \smallskip
        \coloredbullet\ %
        Built documentation and support site with streamlined Slack and Microsoft Teams integrations to enable a small development team to keep up with support demand through
        self-service and more intuitive response vectors.

        \smallskip
        \coloredbullet\ %
        Containerized >15 Laravel sites with Docker Swarm for a B2B consulting agency; cutting deployment time from hours to minutes and eliminating environment drift issues.

        \smallskip
        \coloredbullet\ %
        Built real-time video conferencing platform (Django/NextJS) supporting 500+ concurrent users with WebRTC and Redis pub/sub.

        \smallskip
        \coloredbullet\ %
        Unified CI/CD infrastructure across Azure DevOps, GitHub Actions, and Jenkins, reducing pipeline maintenance overhead substantially.

        \bigskip
    }
%
    \section{Notable Projects}
    %
    \datedexperience{TakePoint (takepoint.dev)}{}
    \explanation{AI-Enhanced Sprint Planning Platform}{}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Built AI-powered sprint planning tool using RAG with OpenAI, generating actionable story breakdowns and retrospective insights in real-time.

        \smallskip
        \coloredbullet\ %
        Engineered bi-directional Jira sync, enabling teams to import backlogs, refine stories with AI assistance, and push changes back without context switching.

        \smallskip
        \coloredbullet\ %
        Reduced OpenAI API costs by 46\% through semantic caching, prompt compression, and intelligent context windowing without degrading output quality.

        \smallskip
        \coloredbullet\ %
        Deployed infrastructure via CloudFormation with self-hosted Docker option for enterprise clients requiring on-premise data residency.

        \smallskip
        \textit{Python, TypeScript, PostgreSQL, MongoDB, CloudFormation, OpenAI, Jira, AWS, Docker}

    }
\end{document}
